The 2018 heatwave and its implications on ozone induced damage on vegetation in a subartic climate

### 2020-03-23 VegOzone.tex
Include the site overviews.
Some plots included. Added text to distribute work load.

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

@@

\introduction  %% \introduction[modified heading if necessary]
\label{sec:intro}
\begin{itemize}
\item ozone in general
\item ozone induced damage in vegetation
\item present subarctic climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] midnight sun and 23\,\unit{h} open stomata (biological details will be published in a compaignend paper)
  \item[$\rightarrow$] ozone climatology and spring peak
  \end{itemize}
\item future climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] increase in heatwaves and dry periodes
  \item[$\rightarrow$] shift in start of growing season (into vincity of ozone spring peak)
  \item[$\rightarrow$] increase in tropospheric background ozone
  \end{itemize}
\end{itemize}

\section{Data}
TEXT

\subsection{NIBIO research station Svanhovd}
TEXT

\subsection{Other observational data}
TEXT

\subsection{Model and reanalysis data}
TEXT

@@

\subsection{Derived climatologies for Svanhovd}
\begin{itemize}
\item temperature
\item precipitation
\item ozone
\end{itemize}

>>>>

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}
\graphicspath{{pictures/}}

@@

\introduction  %% \introduction[modified heading if necessary]
\label{sec:intro}
\begin{itemize}
\item ozone in general
\item ozone induced damage in vegetation \emph{Contributor: Ane - maybe also ask Aud?}
\item present subarctic climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] midnight sun and 23\,\unit{h} open stomata (biological details will be published in a compaignend paper)
  \item[$\rightarrow$] ozone climatology and spring peak
  \end{itemize}
\item future climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] increase in heatwaves and dry periodes
  \item[$\rightarrow$] shift in start of growing season (into vincity of ozone spring peak)
  \item[$\rightarrow$] increase in tropospheric background ozone
  \end{itemize}
\end{itemize}

\section{Data}
TEXT
\begin{figure}[t]
\includegraphics[width=8.3cm]{station_map_fennoscandia}
\caption{Cap of the North. Reasearch stations with given ozone time series in northern Fennoscandia.}
\end{figure}

\subsection{NIBIO research station Svanhovd}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{svanhovd_researchstation}

  \caption{NIBIO research station Svanhovd. Atmospheric monitoring site and ozone garden have been marked in the picture.}
\end{figure}
TEXT: Ozone monitoring and ozone garden. \emph{Invite co-authors from NILU and NIBIO?}

\subsection{Observational data}
Table: EBAS - Station list
\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}

  \caption{Timeseries of ozone observations in northern Fennoscadia. Data taken from EBAS and ozone monitoring at Svanhovd in the summer seasons 2018/19. The hatched area indicates time periods with unsufficient quality control - cite: NILU ozone report 200x.}
\end{figure*}

\subsection{Model and reanalysis data}
TEXT
\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies}

  \caption{Comparison of observational data with various ozone reanlysis products.}
\end{figure}

@@

\subsection{Derived climatologies}
\begin{itemize}
\item temperature
\item precipitation
\item ozone
\end{itemize}
